What We Eval in the Shadows

### 2021-08-12 paper/main.tex
Update 6.extract varargs

\paragraph{Extracting Varargs}
A somewhat odd use of \eval is to obtain the source code of the arguments passed
to a vararg parameter. In this example, the function iterates over the contents
of the vararg until it finds a non-null value. \k{substitute(alist(...))} yields
an expression that represents a call to \k{alist} but where the \k{...} are
expended with the arguments supplied to the function. \Eval then returns a
\k{list} with unevaluated argument expressions which are evaluated sequentially
for their result.

>>>>

\paragraph{Extracting Varargs}
\Eval is to obtain the source code of the arguments passed to a vararg
parameter. One example is a function that iterates over the contents of the
vararg until it finds a non-null value. \k{substitute(alist(...))} yields an
expression that represents a call to \k{alist} but where the \k{...} are
expended with the arguments supplied to the function. \Eval then returns a
\k{list} with unevaluated argument expressions which are evaluated sequentially
for their result. The reason \eval is needed is not to force
any more arguments once a non-null value was found.
